Ternary plots for `hyper2` and `hyper3` samples

### 2024-10-18 inst/ternaryplot_hyper2.Rmd
fixes #137

---
title: "Ternary plots for `hyper2` samples"
author: "Robin Hankin"
output: html_document
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

To cite the `hyper2` package in publications please use @hankin2017_rmd.
Here I show how to use the excellent `Ternary` package [@smith2017] to
generate triangular plots for `hyper2` likelihood functions with size
3.  First load the `Ternary` and `hyper2` packages:

@@

## The `chess` dataset

@@

## The `icons` dataset

@@

>>>>

---
title: "Ternary plots for `hyper2` and `hyper3` samples"
author: "Robin Hankin"
output: html_document
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

To cite the `hyper2` package in publications please use
@hankin2017_rmd.  Here I show how to use the excellent `Ternary`
package [@smith2017] to generate triangular plots for `hyper2` and
`hyper3` likelihood functions with size 3.

First load the `Ternary` and `hyper2` packages:

@@

# The `chess` dataset (`hyper2`)

@@

# The `icons` dataset (`hyper2`)

@@

# Synthetic race data (`hyper3`)

Here we use `rrace3()` to generate repeated results from a race
between three runners.

```{r singlerrace3example}
set.seed(0)
(randomrace <- noquote(rrace3(pn = c(a=6, b=3, c=8), ps = c(a=0.3,b=0.5,c=0.2))))
(S <- ordervec2supp3(randomrace))
maxp(S)
```

Above we see `randomrace` being an order vector for a race with six
`a` clones, 3 `b` clones and 2 `c` clones of PL strengths 0.3, 0.5 and
0.2 respectively.  Thus the first place was a `b`, second place was an
`a`, third place a `c`, and so on.  Object `S` is support function for
this realisation and we also see the maimum likelihood estimate for
the three strengths.  Now we repeatedly run races with these PL
strengths and calculate the maximum likelihood estimate for each
realisation:

```{r repeatedrrace3, cache = TRUE}
x <- t(replicate(50,maxp(ordervec2supp3(rrace3(pn = c(a=16, b=13, c=18), ps = c(a=0.3,b=0.5,c=0.2))))))
```

```{r showx}
head(x)
```

```{r ternaryrrace3}
TernaryPlot(atip="a", btip="b", ctip="c")
TernaryPoints(x, pch=16, cex=0.5)
TernaryPoints(c(0.3,0.5,0.2),pch=16,col="red")
```

Above, we see the ensemble of estimates of the players' Plackett-Luce
strengths as black dots, and the true value of the strengths
(viz. `c(a=0.3,b=0.5,c=0.2)`) in red.  The estimates cluster around the true value.  It might be interesting to assess whether the estimates 
estimates are Dirichlet and, if so, what parameters the distribution
possesses.
